Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2023-12-26 paper.tex
Even more images
Change figure caption

\begin{figure*}[tp]
  \centering
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale-s3.png}
    \label{fig:shale-s3}}
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil.}
  \label{fig:heatmaps}
\end{figure*}

>>>>

\begin{figure*}[tp]
  \centering
  \includegraphics[width=0.4\linewidth]{images/soil-s3.png}
  \hfill
  \includegraphics[width=0.4\linewidth]{images/shale-s3.png}
  \vskip\baselineskip
  \includegraphics[width=0.4\linewidth]{images/soil-avg.png}
  \hfill
  \includegraphics[width=0.4\linewidth]{images/shale-avg.png}
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples. On the
    left: soil, on the right: shale. On the top: the function calculated for a
    rotation of the sample which aligns the direction of anisotropy with the
    axes, on the bottom: the function averaged across 100 random rotations.}
  \label{fig:heatmaps}
\end{figure*}
